---
title: "Home range analysis of kākā at Orokonui Ecosanctuary"
author: "Scott Forrest"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
bibliography: references_11thNov2022.bib
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}

library(knitr)
knitr::opts_chunk$set(echo = TRUE)

```

Load packages and set working directory.

```{r packages, message=FALSE, warning=FALSE}

library(tidyverse)

packages <- c("move", "lattice", "purrr", "here", "raster", "sf", "ggpubr",
              "patchwork", "jtools", "MuMIn", "statmod", "ctmm", "terra")

walk(packages, require, character.only = T)

```

Import data. 

```{r import data, message=FALSE, linewidth = 60}

# create vector of GPS date filenames
GPSfiles <- list.files("CSV input data - dd_speed_6") 

# create a vector for the tag numbers indicating different kākā
id <- 45505:45514

# import data
all_tags_list <- vector(mode = "list", length = length(GPSfiles))

for(i in 1:length(GPSfiles)){
  all_tags_list[[i]] <-  read.csv(paste("CSV input data - dd_speed_6/",
                                             GPSfiles[[i]], 
                                             sep = ""))
  all_tags_list[[i]]$id <- id[i]
}

```

Create an extent raster to be used for each individual. It is important to keep these the same size for the space use variability (SUV) incremental analysis, so it is important that the raster covers the extent of each individual's locations.

```{r set_extent, linewidth = 60}

ext_object <- as(extent(1390000, 1435000, 4910000, 4950000), 'SpatialPolygons')
crs(ext_object) <- "EPSG:2193"
ext_raster <- raster::raster(ext_object, res = 25) # resolution in m

```

Using the ctmm package 

```{r fitting ctmm}

tag_ctmm_list <- vector(mode = "list", length = 10) 
# FIT1_ML_list <- vector(mode = "list", length = 10) 
FIT1_pHREML_list <- vector(mode = "list", length = 10) 
# UD1w_ML_list <- vector(mode = "list", length = 10)
UD1w_pHREML_list <- vector(mode = "list", length = 10)

for(i in 1:10) {

  # create data frames of only necessary info
tag <- all_tags_list[[i]] %>% mutate(ID = id, 
                                     timestamp = DateTime, 
                                     longitude = lon, 
                                     latitude = lat, 
                                     .keep = "none")

# reproject 
tag_ctmm_list[[i]] <- as.telemetry(tag, timezone = "GMT", 
                         projection = paste0("+proj=tmerc +lat_0=0 +lon_0=173 ",
                                             "+k=0.9996 +x_0=1600000 +y_0=10000000 ",
                                             "+ellps=GRS80 +towgs84=0,0,0,0,0,0,0 ",
                                             "+units=m +no_defs +type=crs"))
# plot(tag_ctmm_list[[i]])

level <- 0.95 # we want to display 95% confidence intervals
SVF <- variogram(tag_ctmm_list[[i]])
# plot(SVF, fraction = 1, level = level, 
#      main = paste0("id ", tag_ctmm_list[[i]]@info$identity))

# Estimating the ctmm that is most appropriate for the data

# Calculate an automated model guesstimate:
# ctmm.guess(tag_ctmm_list[[i]], interactive = TRUE)
# using interactive starting estimates
# FIT1_ML_list[[i]] <- ctmm.select(tag_ctmm_list[[i]], GUESS, 
#                        method = 'ML', IC = "AIC", 
#                        verbose = TRUE)


# Calculate an automated model guesstimate:
GUESS1 <- ctmm.guess(tag_ctmm_list[[i]], interactive = FALSE)

# Automated model selection, starting from GUESS:
## reminder: it will default to pHREML if no method is specified.
# FIT1_ML_list[[i]] <- ctmm.select(tag_ctmm_list[[i]], GUESS1, 
#                        method = 'ML', IC = "AIC", 
#                        verbose = TRUE)

# print(summary(FIT1_ML_list[[i]]))

# plot(SVF, CTMM = FIT1_ML_list[[i]][[1]],
#      main = paste0("ML - ", rownames(summary(FIT1_ML_list[[i]]))[1], 
#                    " - ID ", tag_ctmm_list[[i]]@info$identity))
# 
# plot(SVF, CTMM = FIT1_ML_list[[i]][[1]], fraction = 0.02,
#      main = paste0("ML - ", rownames(summary(FIT1_ML_list[[i]]))[1], 
#                    " - ID ", tag_ctmm_list[[i]]@info$identity))

# using pHREML
FIT1_pHREML_list[[i]] <- ctmm.select(tag_ctmm_list[[i]], GUESS1, 
                           method = 'pHREML', IC = "AIC", 
                           verbose = TRUE)

print(summary(FIT1_pHREML_list[[i]]))
# OUa_pHREML <- FIT1_pHREML_list[[i]][[1]]

plot(SVF, CTMM = FIT1_pHREML_list[[i]][[1]], fraction = 1, 
     main = paste0("pHREML - ", rownames(summary(FIT1_pHREML_list[[i]]))[1], 
                   " - ID ", tag_ctmm_list[[i]]@info$identity))

# to view zoomed in plot to assess fit 
# plot(SVF, CTMM = FIT1_pHREML_list[[i]][[1]], fraction = 0.02,
#      main = paste0("pHREML - ", rownames(summary(FIT1_pHREML_list[[i]]))[1],
#                    " - ID ", tag_ctmm_list[[i]]@info$identity))

# Fitting home range model

# Run an area-corrected AKDE with weights:
# UD1w_ML_list[[i]] <- akde(tag_ctmm_list[[i]], FIT1_ML_list[[i]], 
#                           weights = TRUE, grid = ext_raster)
# summary(UD1w_ML_list[[i]])
# summary(UD1_ML)$CI # home range area estimation
# plot(UD1w_ML_list[[i]])
# print(summary(UD1w_ML_list[[i]])$DOF["area"]) # effective sample size of animal1
# print(nrow(tag_ctmm_list[[i]])) # absolute sample size

# Run an area-corrected AKDE with weights using the pHREML estimated model:
UD1w_pHREML_list[[i]] <- akde(tag_ctmm_list[[i]], FIT1_pHREML_list[[i]], 
                              weights = TRUE, grid = ext_raster)

summary(UD1w_pHREML_list[[i]])
plot(UD1w_pHREML_list[[i]])
print(summary(UD1w_pHREML_list[[i]])$DOF["area"]) # effective sample size of animal1
print(nrow(tag_ctmm_list[[i]])) # absolute sample size

}

```

To print any specific outputs.

```{r}

for(i in 1:10) {
# print(summary(UD1w_pHREML_list[[i]]))
# print(summary(UD1w_pHREML_list[[i]])$CI)
# plot(UD1w_pHREML_list[[i]], level.UD = c(0.5, 0.95))
# plot(UD1w_pHREML_list[[i]], level.UD = c(0.5, 0.95))
}

```

Import a spatial object of the Orokonui Ecosanctuary fence.

```{r}

OrokonuiFence <- st_read("mapping/OrokonuiFence.shp")

# check map
ggplot(OrokonuiFence) +
  geom_sf() +
  theme_classic()

```

Extract contours for further analysis.

```{r}

# use the ML estimated UDs
# UD_ctmm_contour_list <- map(UD1w_ML_list, SpatialPolygonsDataFrame.UD, level.UD = c(0.5, 0.95), 
#                             level = 0.95)

# use the perturbative Hybrid REML (pHREML) estimated UDs
UD_ctmm_contour_list <- map(UD1w_pHREML_list, SpatialPolygonsDataFrame.UD, level.UD = c(0.5, 0.95), 
                            level = 0.95)

# create a df with the spatial objects
UD_ctmm_sf <- map(UD_ctmm_contour_list, st_as_sf, crs = 4326) %>% 
  map(., st_transform, crs = 4326) %>% 
  bind_rows() %>% mutate(id = substr(name, start = 1, stop = 5), 
                         age = rep(c(1, 10, 5, 1, 3, 2, 2, 3, 10, 8), each = 6), 
                         contour = substr(name, start = 7, stop = 8),
                         interval = substr(name, start = 11, stop = 13),
                         age_group = ifelse(age < 4, "3 years or younger (n = 6)", "5 years or older (n = 4)"))

UD_ctmm_sf

```


Plotting

```{r}

ggplot() +
  geom_sf(data = UD_ctmm_sf %>% dplyr::filter(contour == 95 & interval == "est"), 
          aes(fill = factor(id)), 
          alpha = 0.2,
               colour = "black", 
               size = 0.25) +
  # to also add the 50% contours - makes it a bit messy in this case
  # geom_sf(data = UD_ctmm_sf %>% dplyr::filter(contour == 50 & interval == "est"), 
  #         # aes(fill = factor(id)), 
  #         alpha = 0,
  #         colour = "black", 
  #         size = 0.25,
  #         linetype = "dashed") +
  geom_sf(data = OrokonuiFence, colour = "black", fill = NA, lwd = 0.5) +
  coord_sf() +
  scale_y_continuous("Latitude", breaks = seq(-45.74, -45.80, by = -0.02)) +
  scale_x_continuous("Longitude", breaks = seq(170.56, 170.62, by = 0.02)) +
  scale_fill_viridis_d(name = "ID") +
  facet_wrap(vars(age_group)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0))) +
  ggspatial::annotation_north_arrow(location = "tr", 
                                    which_north = "true",
                                    height = unit(1, "cm"),
                                    width = unit(.75, "cm")) +
  ggspatial::annotation_scale(location = "br", 
                              style = "ticks",
                              bar_cols = c("grey60", "white"),
                              height = unit(0.25, "cm"))


filetypes <- c("pdf", "tiff", "png")

for(i in 1:length(filetypes)) {
ggsave(filename = paste0("Graphical outputs/",
                       "all_home_ranges_wAKDE_young_old_", Sys.Date(), ".",
                       filetypes[i]),
       width = 160,
       height = 125,
       units = "mm",
       dpi = 300)
}

```

Determine the area contained within the isopleths

```{r}

UD_ctmm_area_50 <- vector(mode = "numeric", length = 10)
UD_ctmm_area_95 <- vector(mode = "numeric", length = 10)

for(i in 1:10) {
  # estimated 50% contour
  UD_ctmm_area_50[[i]] <- UD_ctmm_contour_list[[i]]@polygons[[2]]@area 
  # estimated 95% contour
  UD_ctmm_area_95[[i]] <- UD_ctmm_contour_list[[i]]@polygons[[5]]@area 
}

```

Add additional information about each kākā and create data frame

```{r}

id <- 45505:45514
age <- c(1, 10, 5, 1, 3, 2, 2, 3, 10, 8)
familiarity <- c(1, 10, 5, 1, 3, 2, 2, 3, 1, 8)
sex <- c("M", "M", "M", "F", "F", "F", "F", "M", "M", "F")
origin <- c("Orokonui", "Orokonui", "Captive", "Orokonui", "Orokonui", "Orokonui", 
            "Orokonui",  "Captive", "Captive", "Orokonui")

all_contours_95_df <- data.frame("ID" = id, 
                                 "Age" = age, 
                                 "Familiarity" = familiarity,
                                 "Sex" = sex,
                                 "Origin" = origin,
                                 "UD50_area" = UD_ctmm_area_50, 
                                 "UD95_area" = UD_ctmm_area_95,
                                 "UD50_area_km2" = UD_ctmm_area_50/1e6, 
                                 "UD95_area_km2" = UD_ctmm_area_95/1e6) %>% 
  mutate(age_group = ifelse(Age < 4, "3 years or younger (n = 6)", 
                            "5 years or older (n = 4)"))

head(all_contours_95_df)
max(all_contours_95_df$UD95_area_km2) / min(all_contours_95_df$UD95_area_km2) 
# size difference between largest and smallest UDs = 29 fold-difference

```
Convert to utilisation distributions (continuous probability surfaces).

Calculating the area contained within UD isopleths, which will be in m^2.

Add in individual-level covariates and create a data frame.

Plot

```{r}

all_contours_95_df %>% ggplot(aes(Age, UD95_area_km2)) +
  geom_point(alpha = 0.5, size = 3) +
  scale_x_continuous(breaks = c(1:10)) +
  labs(y = expression(HR[95]~area~(km^2))) +
  theme_classic()

all_contours_95_df %>% ggplot(aes(Familiarity, UD95_area_km2)) +
  geom_point(alpha = 0.5, size = 3) +
  scale_x_continuous(breaks = c(1:10)) +
  labs(y = expression(HR[95]~area~(km^2))) +
  theme_classic()

sexplot <- all_contours_95_df %>% ggplot(aes(Sex, UD95_area_km2)) +
  geom_boxplot(alpha = 0.25, fill = "skyblue") +
  # geom_violin(alpha = 0.25, fill = "skyblue") +
  geom_jitter(width = 0.05, size = 3, alpha = 0.5) +
  labs(y = expression(HR[95]~area~(km^2))) +
  theme_classic()

originplot <- all_contours_95_df %>% ggplot(aes(Origin, UD95_area_km2)) +
  geom_boxplot(alpha = 0.25, fill = "skyblue") +
  # geom_violin(alpha = 0.25, fill = "skyblue") +
  geom_jitter(width = 0.05, size = 3, alpha = 0.5) +
  theme_classic()

ggarrange(sexplot, originplot + rremove("ylab"))

# save objects in multiple filetypes
for(i in 1:length(filetypes)){
ggsave(filename = paste0("Graphical outputs/",
                       "sex_age_plots_", Sys.Date(), ".",
                       filetypes[i]),
       width = 160,
       height = 100,
       units = "mm",
       dpi = 300)
}

```


### Statistical analysis of home range area

Fit the models

```{r}

# four models used for model selection
area_age_glm <- glm(UD95_area_km2 ~ Age, data = all_contours_95_df, family = Gamma(link = "log"))
area_familiarity_glm <- glm(UD95_area_km2 ~ Familiarity, data = all_contours_95_df, family = Gamma(link = "log"))
area_sex_glm <- glm(UD95_area_km2 ~ Sex, data = all_contours_95_df, family = Gamma(link = "log"))
area_origin_glm <- glm(UD95_area_km2 ~ Origin, data = all_contours_95_df, family = Gamma(link = "log"))
area_null_glm <- glm(UD95_area_km2 ~ 1, data = all_contours_95_df, family = Gamma(link = "log"))

```

Model summaries of age model

```{r}

# model with age
summary(area_age_glm)
AIC(area_age_glm) 
anova(area_age_glm,test="F")
r.squaredLR(area_age_glm)
confint(area_age_glm)

```

Model summaries of familiarity model

```{r}

# model with age
summary(area_familiarity_glm)
AIC(area_familiarity_glm) 
anova(area_familiarity_glm,test="F")
r.squaredLR(area_familiarity_glm)
confint(area_familiarity_glm)

```

Model summaries of sex model

```{r}

# model with sex
summary(area_sex_glm)
AIC(area_sex_glm) 
anova(area_sex_glm,test="F")
r.squaredLR(area_sex_glm)
confint(area_sex_glm)

```

Model summaries of origin model

```{r}

# model with kākā origin
summary(area_origin_glm)
AIC(area_origin_glm) 
anova(area_origin_glm,test="F")
r.squaredLR(area_origin_glm)
confint(area_origin_glm)

```

Model summaries of null model

```{r}

# null model (intercept only)
summary(area_null_glm)
AIC(area_null_glm) 
anova(area_null_glm,test="F")
r.squaredLR(area_null_glm)
confint(area_null_glm)

```

As the age model was the only model of interest for inference, check diagnostics and produce plot with fitted model.

```{r}

dfun <- function(object) {
  with(object,sum((weights * residuals^2)[weights > 0])/df.residual)
}

dfun(area_age_glm)
pseudoR2 <- 1 - (area_age_glm$deviance / area_age_glm$null.deviance)
pseudoR2

qr.area_age_glm <- qresid(area_age_glm)
qqnorm(qr.area_age_glm, las = 1)
qqline(qr.area_age_glm)

r<-residuals(area_age_glm,type="pearson")
modfit<-fitted(area_age_glm)

plot(r~modfit, main = "Pearson's Residuals")

par(mfrow=c(1,2)) # change plot window to accommodate 2 plots

r = rstandard(area_age_glm)
lf <- fitted(area_age_glm)
plot(all_contours_95_df$Age, r,xlab="Age",
     ylab="Standardized residual")
abline(h=0)

plot(lf, r,xlab="Fitted values",ylab="Standardized residual")
abline(h=0)

h <- hatvalues(area_age_glm)
cd <- cooks.distance(area_age_glm)
plot(h,cd,xlab="Hat values",ylab="Cook's distance")

par(mfrow=c(1,1)) # return to single plotting

area_age_glm_plot <- effect_plot(area_age_glm, 
                                 pred = Age, 
                                 plot.points = T, 
                                 interval = T, 
                                 point.size = 2.5, 
                                 point.alpha = 0.5) +
  scale_x_continuous("Age", breaks = c(1:10)) +
  ylab(expression(HR[95]~area~(km^2))) +
  theme_classic() +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

area_age_glm_plot

for(i in 1:length(filetypes)){
ggsave(filename = paste0("Graphical outputs/",
                       "age_area_glm_", Sys.Date(), ".",
                       filetypes[i]),
       width = 160,
       height = 100,
       units = "mm",
       dpi = 300)
}

```

Also checking the for familiarity

```{r}

dfun <- function(object) {
  with(object,sum((weights * residuals^2)[weights > 0])/df.residual)
}

dfun(area_familiarity_glm)
pseudoR2 <- 1 - (area_familiarity_glm$deviance / area_familiarity_glm$null.deviance)
pseudoR2

qr.area_familiarity_glm <- qresid(area_familiarity_glm)
qqnorm(qr.area_familiarity_glm, las = 1)
qqline(qr.area_familiarity_glm)

r<-residuals(area_familiarity_glm,type="pearson")
modfit<-fitted(area_familiarity_glm)

plot(r~modfit, main = "Pearson's Residuals")

par(mfrow=c(1,2)) # change plot window to accommodate 2 plots

r = rstandard(area_familiarity_glm)
lf <- fitted(area_familiarity_glm)
plot(all_contours_95_df$Age, r,xlab="Familiarity (years)",
     ylab="Standardized residual")
abline(h=0)

plot(lf, r,xlab="Fitted values",ylab="Standardized residual")
abline(h=0)

h <- hatvalues(area_familiarity_glm)
cd <- cooks.distance(area_familiarity_glm)
plot(h,cd,xlab="Hat values",ylab="Cook's distance")

par(mfrow=c(1,1)) # return to single plotting

area_familiarity_glm_plot <- effect_plot(area_familiarity_glm, 
                                 pred = Familiarity, 
                                 plot.points = T, 
                                 interval = T, 
                                 point.size = 2.5, 
                                 point.alpha = 0.5) +
  scale_x_continuous("Familiarity (years)", breaks = c(1:10)) +
  ylab(expression(HR[95]~area~(km^2))) +
  theme_classic() +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

area_familiarity_glm_plot


for(i in 1:length(filetypes)){
ggsave(filename = paste0("Graphical outputs/",
                       "age_familiarity_glm_", Sys.Date(), ".",
                       filetypes[i]),
       width = 160,
       height = 100,
       units = "mm",
       dpi = 300)
}

```

For checking the overlap between the fence of Orokonui and each UD. This calculation is a summation of the values inside the cells (i.e. the probability), rather than the number of cells, which therefore represent an approximation of the time spent in that area.

```{r}

raster_UD_list <- map(UD1w_pHREML_list, raster, DF = "PMF")
# for(i in 1:10) raster::plot(raster_UD_list[[i]])

# checking that the cell values add up to 1
# for(i in 1:10) print(cellStats(raster_UD_list[[i]], sum))

# testing for a single UD
plot(mask(raster_UD_list[[1]], OrokonuiFence))
cellStats(mask(raster_UD_list[[1]], OrokonuiFence), sum)

inside_overlap <- vector(mode = "numeric", length = 10)

for (i in 1:10){
inside_overlap[[i]] <- cellStats(mask(raster_UD_list[[i]], OrokonuiFence), sum)
print(inside_overlap[[i]])
}

# adding to data frame with inside and outside overlap
all_contours_95_df <- all_contours_95_df %>% 
  mutate(inside = inside_overlap, outside = 1 - inside_overlap)

all_contours_95_df

max(all_contours_95_df$UD95_area_km2) / min(all_contours_95_df$UD95_area_km2)

all_contours_95_df %>% group_by(age_group) %>% summarise(mean_UD50km2 = mean(UD50_area_km2), 
                                 mean_UD95km2 = mean(UD95_area_km2),
                                 meanUD_outside = mean(outside),
                                 sd_UD50km2 = sd(UD50_area_km2), 
                                 sd_UD95km2 = sd(UD95_area_km2),
                                 sdUD_outside = sd(outside))

all_contours_95_df %>% summarise(mean_UD50km2 = mean(UD50_area_km2), 
                                 mean_UD95km2 = mean(UD95_area_km2),
                                 meanUD_inside = mean(inside),
                                 meanUD_outside = mean(outside),
                                 sd_UD50km2 = sd(UD50_area_km2), 
                                 sd_UD95km2 = sd(UD95_area_km2),
                                 sdUD_inside = sd(inside),
                                 sdUD_outside = sd(outside))

```

Plotting home range area, individual-level covariates and overlap with Orokonui Ecosanctuary

```{r}

all_contours_95_df %>% ggplot(aes(x = age, y = outside)) +
  geom_point(size = 2.5, alpha = 0.5) +
  scale_x_continuous(breaks = c(1:10), "Age") +
  scale_y_continuous(breaks = seq(0,1,0.2), limits = c(0,1), 
                     "Proportion of HR Outside of Orokonui Ecosanctaury") +
  theme_classic() +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

```

Statistical analysis using the same methodology as above, for the proportion of area that lies outside of the Orokonui Ecosanctuary fence.

```{r}

outsideglm <- glm(outside ~ age, 
                  data = all_contours_95_df, 
                  family = Gamma(link = "log"))

summary(outsideglm)
AIC(outsideglm)
anova(outsideglm,test="F")
r.squaredLR(outsideglm)
confint(outsideglm)

dfun <- function(object) {
  with(object,sum((weights * residuals^2)[weights > 0])/df.residual)
}

dfun(outsideglm)
pseudoR2 <- 1 - (outsideglm$deviance / outsideglm$null.deviance)
pseudoR2

qr.outsideglm <- qresid(outsideglm)
qqnorm(qr.outsideglm, las = 1)
qqline(qr.outsideglm)

r<-residuals(outsideglm,type="pearson")
modfit<-fitted(outsideglm)

plot(r~modfit, main = "Pearson's Residuals")

par(mfrow=c(1,2)) # change plot window to accommodate 2 plots

r = rstandard(outsideglm)
lf <- fitted(outsideglm)
plot(all_contours_95_df$Age, r,xlab="Age",
     ylab="Standardized residual")
abline(h=0)

plot(lf, r,xlab="Fitted values",ylab="Standardized residual")
abline(h=0)

h <- hatvalues(outsideglm)
cd <- cooks.distance(outsideglm)
plot(h,cd,xlab="Hat values",ylab="Cook's distance")

par(mfrow=c(1,1)) # return to single plotting

outsideglmplot <- effect_plot(outsideglm, 
                              pred = age, 
                              plot.points = T, 
                              interval = T, 
                              point.size = 2.5, 
                              point.alpha = 0.5) +
  scale_x_continuous(breaks = c(1:10)) +
  labs(x = "Age", y = "Proportion of HR Outside of Orokonui") +
  theme_classic() +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

outsideglmplot

ggarrange(area_age_glm_plot, outsideglmplot, labels = "AUTO", label.x = 0.55)

for(i in 1:length(filetypes)) {
ggsave(filename = paste0("Graphical outputs/",
                       "age_area_overlap_glms_", Sys.Date(), ".",
                       filetypes[i]),
       width = 160,
       height = 100,
       units = "mm",
       dpi = 300)
}

```

```{r}

ggarrange(area_age_glm_plot, area_familiarity_glm_plot, labels = "AUTO", label.x = 0.55)

for(i in 1:length(filetypes)) {
ggsave(filename = paste0("Graphical outputs/",
                       "age_area_familiarity_glms_", Sys.Date(), ".",
                       filetypes[i]),
       width = 160,
       height = 100,
       units = "mm",
       dpi = 300)
}

```


### References

<div id="refs"></div>

### Session info

```{r}

sessionInfo()

```