---
title: "Home range analysis of kākā at Orokonui Ecosanctuary"
author: "Scott Forrest"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
bibliography: references_20240315.bib
editor_options: 
  chunk_output_type: inline
---

In this script we are fitting home range models to GPS data of kākā (Nestor meridionalis) at Orokonui Ecosanctuary, New Zealand. We are fitting data across the whole tracking period to estimate their long-term space use.

```{r setup, include=FALSE}

library(knitr)
knitr::opts_chunk$set(echo = TRUE)

```

## Load packages and set working directory.

```{r packages, warning=FALSE}

library(tidyverse)

packages <- c("move", "lattice", "purrr", "here", "raster", "sf", "ggpubr",
              "patchwork", "jtools", "MuMIn", "statmod", "ctmm", "terra")

walk(packages, require, character.only = T)

```

## Import data. 

```{r import data, message=FALSE, linewidth = 60}

# create vector of GPS date filenames
GPSfiles <- list.files("CSV input data - dd_speed_6") 

# create a vector for the tag numbers indicating different kākā
id <- 45505:45514

# import data
all_tags_list <- vector(mode = "list", length = length(GPSfiles))

for(i in 1:length(GPSfiles)){
  all_tags_list[[i]] <-  read.csv(paste("CSV input data - dd_speed_6/",
                                             GPSfiles[[i]], 
                                             sep = ""))
  all_tags_list[[i]]$id <- id[i]
}

```

Create an extent raster to be used for each individual. It is important to keep these the same size for the dynamic space use incremental analysis, so it is important that the raster covers the extent of each individual's locations.

```{r set_extent, linewidth = 60}

ext_object <- as(extent(1390000, 1435000, 4910000, 4950000), 'SpatialPolygons')
crs(ext_object) <- "EPSG:2193"
ext_raster <- raster::raster(ext_object, res = 25) # resolution in m

```

# Fit home range models

Using the ctmm package to fit continuous-time movement models to the data. 

We are mostly following the step-by-step approach presented by @Silva2022-rf, Supplementary Materials 2.

To determine the best model for **each individual**, we start by using the ctmm.guess function. This gets starting values for the ctmm.select function, which is used for model selection. We then fit the best model for each individual using the `akde` function. We do this for each individual by looping over each one. We leave commented out code here to show the diagnostic and model checking steps that we took to ensure that the model fits were suitable for each individual's data, such as trying to fit models with the **pHREML** method, and using the **ML** method. We also check the variogram of the data for each individual.

```{r fitting ctmm, cache = TRUE}

tag_ctmm_list <- vector(mode = "list", length = 10) 
# FIT1_ML_list <- vector(mode = "list", length = 10) 
FIT1_pHREML_list <- vector(mode = "list", length = 10) 
# UD1w_ML_list <- vector(mode = "list", length = 10)
UD1w_pHREML_list <- vector(mode = "list", length = 10)

for(i in 1:10) {

  # create data frames of only necessary information
tag <- all_tags_list[[i]] %>% mutate(ID = id, 
                                     timestamp = DateTime, 
                                     longitude = lon, 
                                     latitude = lat, 
                                     .keep = "none")

# reproject 
tag_ctmm_list[[i]] <- as.telemetry(tag, timezone = "GMT", 
                         projection = paste0("+proj=tmerc +lat_0=0 +lon_0=173 ",
                                             "+k=0.9996 +x_0=1600000 +y_0=10000000 ",
                                             "+ellps=GRS80 +towgs84=0,0,0,0,0,0,0 ",
                                             "+units=m +no_defs +type=crs"))
# plot(tag_ctmm_list[[i]])

level <- 0.95 # we want to display 95% confidence intervals
SVF <- variogram(tag_ctmm_list[[i]])
# plot(SVF, fraction = 1, level = level, 
#      main = paste0("id ", tag_ctmm_list[[i]]@info$identity))

# Estimating the ctmm that is most appropriate for the data

# Calculate an automated model guesstimate:
# ctmm.guess(tag_ctmm_list[[i]], interactive = TRUE)
# using interactive starting estimates
# FIT1_ML_list[[i]] <- ctmm.select(tag_ctmm_list[[i]], GUESS, 
#                        method = 'ML', IC = "AIC", 
#                        verbose = TRUE)


# Calculate an automated model guesstimate:
GUESS1 <- ctmm.guess(tag_ctmm_list[[i]], interactive = FALSE)

# Automated model selection, starting from GUESS:
## reminder: it will default to pHREML if no method is specified.
# FIT1_ML_list[[i]] <- ctmm.select(tag_ctmm_list[[i]], GUESS1, 
#                        method = 'ML', IC = "AIC", 
#                        verbose = TRUE)

# print(summary(FIT1_ML_list[[i]]))

# plot(SVF, CTMM = FIT1_ML_list[[i]][[1]],
#      main = paste0("ML - ", rownames(summary(FIT1_ML_list[[i]]))[1], 
#                    " - ID ", tag_ctmm_list[[i]]@info$identity))
# 
# plot(SVF, CTMM = FIT1_ML_list[[i]][[1]], fraction = 0.02,
#      main = paste0("ML - ", rownames(summary(FIT1_ML_list[[i]]))[1], 
#                    " - ID ", tag_ctmm_list[[i]]@info$identity))

# using pHREML
FIT1_pHREML_list[[i]] <- ctmm.select(tag_ctmm_list[[i]], GUESS1, 
                           method = 'pHREML', IC = "AIC", 
                           verbose = TRUE)

print(summary(FIT1_pHREML_list[[i]]))
# OUa_pHREML <- FIT1_pHREML_list[[i]][[1]]

plot(SVF, CTMM = FIT1_pHREML_list[[i]][[1]], fraction = 1, 
     main = paste0("pHREML - ", rownames(summary(FIT1_pHREML_list[[i]]))[1], 
                   " - ID ", tag_ctmm_list[[i]]@info$identity))

# to view zoomed in plot to assess fit 
# plot(SVF, CTMM = FIT1_pHREML_list[[i]][[1]], fraction = 0.02,
#      main = paste0("pHREML - ", rownames(summary(FIT1_pHREML_list[[i]]))[1],
#                    " - ID ", tag_ctmm_list[[i]]@info$identity))

# Fitting home range model

# Run an area-corrected AKDE with weights:
# UD1w_ML_list[[i]] <- akde(tag_ctmm_list[[i]], FIT1_ML_list[[i]], 
#                           weights = TRUE, grid = ext_raster)
# summary(UD1w_ML_list[[i]])
# summary(UD1_ML)$CI # home range area estimation
# plot(UD1w_ML_list[[i]])
# print(summary(UD1w_ML_list[[i]])$DOF["area"]) # effective sample size of animal1
# print(nrow(tag_ctmm_list[[i]])) # absolute sample size

# Run an area-corrected AKDE with weights using the pHREML estimated model:
UD1w_pHREML_list[[i]] <- akde(tag_ctmm_list[[i]], FIT1_pHREML_list[[i]], 
                              weights = TRUE, grid = ext_raster)

summary(UD1w_pHREML_list[[i]])
plot(UD1w_pHREML_list[[i]])
print(summary(UD1w_pHREML_list[[i]])$DOF["area"]) # effective sample size of animal1
print(nrow(tag_ctmm_list[[i]])) # absolute sample size

}

```

To print any specific outputs.

These are commnented out but uncomment to view results (if the objects have been created).

```{r}

for(i in 1:10) {
# print(summary(UD1w_pHREML_list[[i]]))
# print(summary(UD1w_pHREML_list[[i]])$CI)
# plot(UD1w_pHREML_list[[i]], level.UD = c(0.5, 0.95))
# plot(UD1w_pHREML_list[[i]], level.UD = c(0.5, 0.95))
}

```

Import a spatial object of the Orokonui Ecosanctuary fence.

```{r}

OrokonuiFence <- st_read("mapping/OrokonuiFence.shp")

# check map
ggplot(OrokonuiFence) +
  geom_sf() +
  theme_classic()

```

Extract contours for further analysis.

```{r}

# use the ML estimated UDs
# UD_ctmm_contour_list <- map(UD1w_ML_list, SpatialPolygonsDataFrame.UD,
#                             level.UD = c(0.5, 0.95),
#                             level = 0.95)

# use the perturbative Hybrid REML (pHREML) estimated UDs
UD_ctmm_contour_list <- map(UD1w_pHREML_list, SpatialPolygonsDataFrame.UD, 
                            level.UD = c(0.5, 0.95), 
                            level = 0.95)

# create a df with the spatial objects
UD_ctmm_sf <- map(UD_ctmm_contour_list, st_as_sf, crs = 4326) %>% 
  map(., st_transform, crs = 4326) %>% 
  bind_rows() %>% mutate(id = substr(name, start = 1, stop = 5), 
                         age = rep(c(1, 10, 5, 1, 3, 2, 2, 3, 10, 8), each = 6), 
                         contour = substr(name, start = 7, stop = 8),
                         interval = substr(name, start = 11, stop = 13),
                         age_group = ifelse(age < 4, 
                                            "3 years or younger (n = 6)", 
                                            "5 years or older (n = 4)"))

UD_ctmm_sf

```

## Plotting for manuscript

```{r}

ggplot() +
  geom_sf(data = UD_ctmm_sf %>% dplyr::filter(contour == 95 & interval == "est"), 
          aes(fill = factor(id)), 
          alpha = 0.2,
               colour = "black", 
               size = 0.25) +
  # to also add the 50% contours - makes it a bit messy in this case
  # geom_sf(data = UD_ctmm_sf %>% dplyr::filter(contour == 50 & interval == "est"), 
  #         # aes(fill = factor(id)), 
  #         alpha = 0,
  #         colour = "black", 
  #         size = 0.25,
  #         linetype = "dashed") +
  geom_sf(data = OrokonuiFence, colour = "black", fill = NA, lwd = 0.5) +
  coord_sf() +
  scale_y_continuous("Latitude", breaks = seq(-45.74, -45.80, by = -0.02)) +
  scale_x_continuous("Longitude", breaks = seq(170.56, 170.62, by = 0.02)) +
  scale_fill_viridis_d(name = "ID") +
  facet_wrap(vars(age_group)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0))) +
  ggspatial::annotation_north_arrow(location = "tr", 
                                    which_north = "true",
                                    height = unit(1, "cm"),
                                    width = unit(.75, "cm")) +
  ggspatial::annotation_scale(location = "br", 
                              style = "ticks",
                              bar_cols = c("grey60", "white"),
                              height = unit(0.25, "cm"))


filetypes <- c("pdf", "tiff", "jpeg", "png")

for(i in 1:length(filetypes)) {
ggsave(filename = paste0("Graphical outputs/",
                       "all_home_ranges_wAKDE_young_old_", Sys.Date(), ".",
                       filetypes[i]),
       width = 180,
       height = 150,
       units = "mm",
       dpi = 800)
}

```

## Determine the area contained within the isopleths

```{r}

UD_ctmm_area_50 <- vector(mode = "numeric", length = 10)
UD_ctmm_area_95 <- vector(mode = "numeric", length = 10)

for(i in 1:10) {
  # estimated 50% contour
  UD_ctmm_area_50[[i]] <- UD_ctmm_contour_list[[i]]@polygons[[2]]@area 
  # estimated 95% contour
  UD_ctmm_area_95[[i]] <- UD_ctmm_contour_list[[i]]@polygons[[5]]@area 
}

```

## Add additional information about each kākā and create data frame

Familiarity is the number of years that a kākā had been in Orokonui Ecosanctuary, as we were trying to determine whether the kākā's age was leading to small home ranges, or whether it was how long each kākā had been in Orokonui, as we thought that individuals which had been recently released in Orokonui might have been more exploratory, even though they were older. For most individuals their age is the same as their familiarity, as they fledged in Orokonui or were released as juveniles, but there is one 10 year old individual that was released as an adult. This individual had a very small home range, which gave more weight to the 'age' hypothesis rather than 'familiarity'.

```{r}

id <- 45505:45514
age <-          c(1, 10, 5, 1, 3, 2, 2, 3, 10, 8)
familiarity <-  c(1, 10, 5, 1, 3, 2, 2, 3, 1,  8)
sex <- c("M", "M", "M", "F", "F", "F", "F", "M", "M", "F")
origin <- c("Orokonui", "Orokonui", "Captive", "Orokonui", "Orokonui", "Orokonui", 
            "Orokonui",  "Captive", "Captive", "Orokonui")

all_contours_95_df <- data.frame("ID" = id, 
                                 "Age" = age, 
                                 "Familiarity" = familiarity,
                                 "Sex" = sex,
                                 "Origin" = origin,
                                 "UD50_area" = UD_ctmm_area_50, 
                                 "UD95_area" = UD_ctmm_area_95,
                                 "UD50_area_km2" = UD_ctmm_area_50/1e6, 
                                 "UD95_area_km2" = UD_ctmm_area_95/1e6) %>% 
  mutate(age_group = ifelse(Age < 4, "3 years or younger (n = 6)", 
                            "5 years or older (n = 4)"))

head(all_contours_95_df)
max(all_contours_95_df$UD95_area_km2) / min(all_contours_95_df$UD95_area_km2) 
# size difference between largest and smallest UDs = 29 fold-difference

```

## Convert to utilisation distributions (continuous probability surfaces).

Calculating the area contained within UD isopleths, which will be in m^2.

Add in individual-level covariates and create a data frame.

### Plot

```{r}

all_contours_95_df %>% ggplot(aes(Age, UD95_area_km2)) +
  geom_point(alpha = 0.5, size = 3) +
  scale_x_continuous(breaks = c(1:10)) +
  labs(y = expression(HR[95]~area~(km^2))) +
  theme_classic()

all_contours_95_df %>% ggplot(aes(Familiarity, UD95_area_km2)) +
  geom_point(alpha = 0.5, size = 3) +
  scale_x_continuous(breaks = c(1:10)) +
  labs(y = expression(HR[95]~area~(km^2))) +
  theme_classic()

sexplot <- all_contours_95_df %>% ggplot(aes(Sex, UD95_area_km2)) +
  geom_boxplot(alpha = 0.25, fill = "skyblue") +
  # geom_violin(alpha = 0.25, fill = "skyblue") +
  geom_jitter(width = 0.05, size = 3, alpha = 0.5) +
  labs(y = expression(HR[95]~area~(km^2))) +
  theme_classic()

originplot <- all_contours_95_df %>% ggplot(aes(Origin, UD95_area_km2)) +
  geom_boxplot(alpha = 0.25, fill = "skyblue") +
  # geom_violin(alpha = 0.25, fill = "skyblue") +
  geom_jitter(width = 0.05, size = 3, alpha = 0.5) +
  theme_classic()

ggarrange(sexplot, originplot + rremove("ylab"))

# save objects in multiple filetypes
for(i in 1:length(filetypes)){
ggsave(filename = paste0("Graphical outputs/",
                       "sex_age_plots_", Sys.Date(), ".",
                       filetypes[i]),
       width = 160,
       height = 100,
       units = "mm",
       dpi = 800)
}

```

# Statistical analysis of home range area

Now that we have extracted the area from the contours, we can use those values in statistical models such as GLMs, to assess whether there are any significant differences in home range area due to factors such as age and sex.

## Fit the models

```{r}

# four models used for model selection
area_age_glm <- glm(UD95_area_km2 ~ Age, 
                    data = all_contours_95_df, 
                    family = Gamma(link = "log"))

area_familiarity_glm <- glm(UD95_area_km2 ~ Familiarity, 
                            data = all_contours_95_df, 
                            family = Gamma(link = "log"))

area_sex_glm <- glm(UD95_area_km2 ~ Sex, 
                    data = all_contours_95_df, 
                    family = Gamma(link = "log"))

area_origin_glm <- glm(UD95_area_km2 ~ Origin, 
                       data = all_contours_95_df, 
                       family = Gamma(link = "log"))

area_null_glm <- glm(UD95_area_km2 ~ 1, 
                     data = all_contours_95_df, 
                     family = Gamma(link = "log"))

```

### Model summaries of age model

```{r}

# model with age
summary(area_age_glm)
AIC(area_age_glm) 
anova(area_age_glm,test="F")
r.squaredLR(area_age_glm)
confint(area_age_glm)

```

### Model summaries of familiarity model

```{r}

# model with age
summary(area_familiarity_glm)
AIC(area_familiarity_glm) 
anova(area_familiarity_glm,test="F")
r.squaredLR(area_familiarity_glm)
confint(area_familiarity_glm)

```

### Model summaries of sex model

```{r}

# model with sex
summary(area_sex_glm)
AIC(area_sex_glm) 
anova(area_sex_glm,test="F")
r.squaredLR(area_sex_glm)
confint(area_sex_glm)

```

### Model summaries of origin model

```{r}

# model with kākā origin
summary(area_origin_glm)
AIC(area_origin_glm) 
anova(area_origin_glm,test="F")
r.squaredLR(area_origin_glm)
confint(area_origin_glm)

```

### Model summaries of null model

```{r}

# null model (intercept only)
summary(area_null_glm)
AIC(area_null_glm) 
anova(area_null_glm,test="F")
r.squaredLR(area_null_glm)
confint(area_null_glm)

```

## Model diagnostics 

Only the age and familiarity models were significant, but as they were competing hypotheses we chose one, which was the age model, as it explains the data better (the older individual that was released into Orokonui had a small home range), and has a higher R-squared. We therefore check model diagnostics and produce a plot with fitted model. 

```{r}

dfun <- function(object) {
  with(object,sum((weights * residuals^2)[weights > 0])/df.residual)
}

dfun(area_age_glm)
pseudoR2 <- 1 - (area_age_glm$deviance / area_age_glm$null.deviance)
pseudoR2

qr.area_age_glm <- qresid(area_age_glm)
qqnorm(qr.area_age_glm, las = 1)
qqline(qr.area_age_glm)

r<-residuals(area_age_glm,type="pearson")
modfit<-fitted(area_age_glm)

plot(r~modfit, main = "Pearson's Residuals")

par(mfrow=c(1,2)) # change plot window to accommodate 2 plots

r = rstandard(area_age_glm)
lf <- fitted(area_age_glm)
plot(all_contours_95_df$Age, r,xlab="Age",
     ylab="Standardized residual")
abline(h=0)

plot(lf, r,xlab="Fitted values",ylab="Standardized residual")
abline(h=0)

h <- hatvalues(area_age_glm)
cd <- cooks.distance(area_age_glm)
plot(h,cd,xlab="Hat values",ylab="Cook's distance")

par(mfrow=c(1,1)) # return to single plotting

area_age_glm_plot <- effect_plot(area_age_glm, 
                                 pred = Age, 
                                 plot.points = T, 
                                 interval = T, 
                                 point.size = 2.5, 
                                 point.alpha = 0.5) +
  scale_x_continuous("Age", breaks = c(1:10)) +
  ylab(expression(HR[95]~area~(km^2))) +
  theme_classic() +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

area_age_glm_plot

for(i in 1:length(filetypes)){
ggsave(filename = paste0("Graphical outputs/",
                       "age_area_glm_", Sys.Date(), ".",
                       filetypes[i]),
       width = 160,
       height = 100,
       units = "mm",
       dpi = 800)
}

```

We also check the diagnostics and create a plot for the familiarity model.

```{r}

dfun <- function(object) {
  with(object,sum((weights * residuals^2)[weights > 0])/df.residual)
}

dfun(area_familiarity_glm)
pseudoR2 <- 1 - (area_familiarity_glm$deviance / area_familiarity_glm$null.deviance)
pseudoR2

qr.area_familiarity_glm <- qresid(area_familiarity_glm)
qqnorm(qr.area_familiarity_glm, las = 1)
qqline(qr.area_familiarity_glm)

r<-residuals(area_familiarity_glm,type="pearson")
modfit<-fitted(area_familiarity_glm)

plot(r~modfit, main = "Pearson's Residuals")

par(mfrow=c(1,2)) # change plot window to accommodate 2 plots

r = rstandard(area_familiarity_glm)
lf <- fitted(area_familiarity_glm)
plot(all_contours_95_df$Age, r,xlab="Familiarity (years)",
     ylab="Standardized residual")
abline(h=0)

plot(lf, r,xlab="Fitted values",ylab="Standardized residual")
abline(h=0)

h <- hatvalues(area_familiarity_glm)
cd <- cooks.distance(area_familiarity_glm)
plot(h,cd,xlab="Hat values",ylab="Cook's distance")

par(mfrow=c(1,1)) # return to single plotting

area_familiarity_glm_plot <- effect_plot(area_familiarity_glm, 
                                 pred = Familiarity, 
                                 plot.points = T, 
                                 interval = T, 
                                 point.size = 2.5, 
                                 point.alpha = 0.5) +
  scale_x_continuous("Familiarity (years)", breaks = c(1:10)) +
  ylab(expression(HR[95]~area~(km^2))) +
  theme_classic() +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

area_familiarity_glm_plot


for(i in 1:length(filetypes)){
ggsave(filename = paste0("Graphical outputs/",
                       "age_familiarity_glm_", Sys.Date(), ".",
                       filetypes[i]),
       width = 160,
       height = 100,
       units = "mm",
       dpi = 800)
}

```

# Calculate the overlap between the UD and the Orokonui Ecosanctuary fence

For checking the overlap between the fence of Orokonui and each UD. This calculation is a *summation of the values inside the cells* (i.e. the probability values), rather than the number of cells, as we want to approximate the time each kākā spent inside the sanctuary.

```{r}

raster_UD_list <- map(UD1w_pHREML_list, raster, DF = "PMF")
# for(i in 1:10) raster::plot(raster_UD_list[[i]])

# checking that the cell values add up to 1
# for(i in 1:10) print(cellStats(raster_UD_list[[i]], sum))

# testing for a single UD
plot(mask(raster_UD_list[[1]], OrokonuiFence))
cellStats(mask(raster_UD_list[[1]], OrokonuiFence), sum)

inside_overlap <- vector(mode = "numeric", length = 10)

for (i in 1:10){
inside_overlap[[i]] <- cellStats(mask(raster_UD_list[[i]], OrokonuiFence), sum)
print(inside_overlap[[i]])
}

# adding to data frame with inside and outside overlap
all_contours_95_df <- all_contours_95_df %>% 
  mutate(inside = inside_overlap, outside = 1 - inside_overlap)

all_contours_95_df

max(all_contours_95_df$UD95_area_km2) / min(all_contours_95_df$UD95_area_km2)

all_contours_95_df %>% group_by(age_group) %>% 
  summarise(mean_UD50km2 = mean(UD50_area_km2), 
            mean_UD95km2 = mean(UD95_area_km2),
            meanUD_outside = mean(outside),
            sd_UD50km2 = sd(UD50_area_km2), 
            sd_UD95km2 = sd(UD95_area_km2),
            sdUD_outside = sd(outside))

all_contours_95_df %>% summarise(mean_UD50km2 = mean(UD50_area_km2), 
                                 mean_UD95km2 = mean(UD95_area_km2),
                                 meanUD_inside = mean(inside),
                                 meanUD_outside = mean(outside),
                                 sd_UD50km2 = sd(UD50_area_km2), 
                                 sd_UD95km2 = sd(UD95_area_km2),
                                 sdUD_inside = sd(inside),
                                 sdUD_outside = sd(outside))

```

### Plotting home range area, individual-level covariates and overlap with Orokonui Ecosanctuary

```{r}

all_contours_95_df %>% ggplot(aes(x = age, y = outside)) +
  geom_point(size = 2.5, alpha = 0.5) +
  scale_x_continuous(breaks = c(1:10), "Age") +
  scale_y_continuous(breaks = seq(0,1,0.2), limits = c(0,1), 
                     "HR Outside of Orokonui Ecosanctaury") +
  theme_classic() +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

```

Statistical analysis using the same methodology as above, for the *proportion of area that lies outside of the Orokonui Ecosanctuary fence*.

```{r}

outsideglm <- glm(outside ~ age, 
                  data = all_contours_95_df, 
                  family = Gamma(link = "log"))

summary(outsideglm)
AIC(outsideglm)
anova(outsideglm,test="F")
r.squaredLR(outsideglm)
confint(outsideglm)

dfun <- function(object) {
  with(object,sum((weights * residuals^2)[weights > 0])/df.residual)
}

dfun(outsideglm)
pseudoR2 <- 1 - (outsideglm$deviance / outsideglm$null.deviance)
pseudoR2

qr.outsideglm <- qresid(outsideglm)
qqnorm(qr.outsideglm, las = 1)
qqline(qr.outsideglm)

r<-residuals(outsideglm,type="pearson")
modfit<-fitted(outsideglm)

plot(r~modfit, main = "Pearson's Residuals")

par(mfrow=c(1,2)) # change plot window to accommodate 2 plots

r = rstandard(outsideglm)
lf <- fitted(outsideglm)
plot(all_contours_95_df$Age, r,xlab="Age",
     ylab="Standardized residual")
abline(h=0)

plot(lf, r,xlab="Fitted values",ylab="Standardized residual")
abline(h=0)

h <- hatvalues(outsideglm)
cd <- cooks.distance(outsideglm)
plot(h,cd,xlab="Hat values",ylab="Cook's distance")

```

### Plot the age model results and overlap model results together

```{r}

par(mfrow=c(1,1)) # return to single plotting

outsideglmplot <- effect_plot(outsideglm, 
                              pred = age, 
                              plot.points = T, 
                              interval = T, 
                              point.size = 2.5, 
                              point.alpha = 0.5) +
  scale_x_continuous(breaks = c(1:10)) +
  # scale_y_continuous(limits = c(0,1)) +
  coord_cartesian(ylim = c(0, 1), xlim = c(1,10)) +
  labs(x = "Age", y = "HR Outside of Orokonui") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  theme_classic() +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

outsideglmplot

ggarrange(area_age_glm_plot, outsideglmplot) # , labels = "AUTO", label.x = 0.55

for(i in 1:length(filetypes)) {
ggsave(filename = paste0("Graphical outputs/",
                       "age_area_overlap_glms_", Sys.Date(), ".",
                       filetypes[i]),
       width = 180,
       height = 50,
       units = "mm",
       dpi = 800)
}

```

### Compare the age model results and familiarity model results together

```{r}

ggarrange(area_age_glm_plot, area_familiarity_glm_plot, 
          labels = "AUTO", label.x = 0.55)

for(i in 1:length(filetypes)) {
ggsave(filename = paste0("Graphical outputs/",
                       "age_area_familiarity_glms_", Sys.Date(), ".",
                       filetypes[i]),
       width = 160,
       height = 100,
       units = "mm",
       dpi = 800)
}

```

### References

<div id="refs"></div>

### Session info

```{r}

sessionInfo()

```